---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dnasim

<!-- badges: start -->
<!-- badges: end -->

A XOR encoding algorithm in R, based on [Sharma et al. (2020)](https://doi.org/10.1049/iet-nbt.2020.0157).

## Installation

You can install the development version of dnasim from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("omunizb/dnasim")
```

## Encoding of data to DNA and its retrieval

The functions `encoding_XOR()` and `retrieval_XOR()` can be used to simulate the DNA-based data storage process using the XOR algorithm as a method for error correction:

```{r example}
library(dnasim)
encoding_XOR(example_bin, example_codevect, "../fragments.fa")
retrieval_XOR("../fragments.fa", example_codevect)
```

Other functions from `dnasim` that may prove useful outside of this specific application are `pdf_print()` and `add_error()`. The first is useful to split long strings so that they do not surpass the margins of PDF output files such as R Markdown knit, whereas the second simulates errors in DNA, changing some of its nucleotides using a user-provided error rate.

```{r}
DNAseq <- c("C", "G", "T", "G", "T", "A", "G", "A", "A", "T", "G", "T", "C")
add_error(DNAseq, 0.05)
```

Finally, there are also functions proveded in the package that encable the conversion from binary to quaternary DNA code, and vice versa.
